%!TEX root = ../../ThesisRomainbrault.tex
% Acknowledgements

% Bookmark name visible in a PDF viewer
\pdfbookmark[1]{Acknowledgements}{Acknowledgements}

\begin{flushright}{\slshape
``We have at our command computers with adequate data-handling ability and with
sufficient computational speed to make use of machine-learning techniques, \\
but our knowledge of the basic principles of these techniques is still
rudimentary. \\
Lacking such knowledge, it is necessary to specify methods of
problem solution in minute and exact detail, \\
a time-consuming and costly procedure. \\
Programming computers to learn from experience should eventually
eliminate the need for much of this detailed programming effort.'' \\
--- \defcitealias{samuel1959some}{Arthur Samuel}\citetalias{samuel1959some}
\citep{samuel1959some}}
\end{flushright}

\bigskip

%----------------------------------------------------------------------------------------

\begingroup

\let\clearpage\relax
\let\cleardoublepage\relax
\let\cleardoublepage\relax

\chapter*{Acknowledgements}

First of all I would like to express my sincere gratitude to my advisor Prof.
Florence d'Alch\'e-Buc for guiding me, the continuous support during this
Ph.~D thesis and her insightful remarks.
\paragraph{}
Besides my advisor, I would also like to thank my thesis jury Prof. Liva
Ralaivola and Prof. Paul Honeine.
\paragraph{}
This thesis would not have been possible without my collaborators Dr. Markus
Heinonen and Dr. Maxime Sangnier, whose help have been precious to developp
fully my ideas and publish. I would like to thank Dr. Nicolas Goix, Dr. Nicolas
Drougard and Ma\"el Chiapino with whom it has been a pleasure to collaborate on
a paper.
\paragraph{}
I would also like to acknowledge the Universit\'e d'\'Evry-val-d'Essonne for
hosting and funding\footnote{PhD grant numbered 76391} me for the first part
of my thesis and T\'el\'ecom PariTech for the second part.

\endgroup

\chapterend
